Precise predictions for same-sign W-bosons scattering at the LHC

### 2017-12-15 Draft/contributions.tex
added EPJC template
contributions.tex: text added

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential distribution in the di-jet invariant mass (left) and the difference of the jet rapidity (right) at LO.
No cuts on the di-jet invariant mass and the different of the jet rapidity are applied.}
\label{fig:mjjdyjj_1d}
\end{figure}

>>>>

At tree--level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha_{ew}^6)$, the QCD background $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ and the interference $\mathcal{O}(\alpha_s\alpha_{ew}^5)$.\\
Concerning the QCD contribution, it is worth noticing that for quantum numbers conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ diagrams only involve $t/u$--channel virtual gluons.\\

The three contributions to the the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential distribution in the jet--jet invariant mass $M_{jj}$ (left) and the positive difference of the jet rapidities $|\Delta y_{jj}|$ (right) at LO. EW contribution in red, QCD in green, interference in gray and sum in blue. No cuts on $M_{jj}$ and $|\Delta y_{jj}|$ are applied.}
\label{fig:mjjdyjj_1d}
\end{figure*}
The interference between EW and QCD contributions is small [to be commented further]
